Continuous Generalization of Buildings

### 2017-05-16 ContinuousGeneralisation_Paper/ContinuousGeneralisation_Paper_Springer/ContinuousGeneralisation_Paper_Springer.tex
finished implementing the target forms of the buildings; removed some old results

Geometric Simplication of Administrative Borders With Mixture of
Irregular and Orthogonal Segments \parencite{Samsonov2016}

@@

>>>>

Geometric Simplification of Administrative Borders With Mixture 
of
Irregular and Orthogonal Segments \parencite{Samsonov2016}

@@

An example of enlargement in aggregation: \citetitle{Neun2005}

Using MST to group buildings: \textcite{Zhang2013, 
Cetinkaya2015,Deng2017,Regnauld1996}
